\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-09 paper/draft.tex
Fix todos

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/pash_overview.pdf}}
\caption{
  \textbf{\sys overview and correspondence to sections.}
  \sys identifies dataflow regions~\sx{dataflow-regions}, 
  converts them to a dataflow graph~\sx{graph-components}, applies iterative
  transformations~\sx{ir:transformations} based on the parallelizability properties (\S\ref{cmd}, \S\ref{ext}) 
  of the commands used in these regions, and finally emits a parallel script
  that uses custom primitives~\sx{optimizer}.
}
\vspace{-25pt}
\label{fig:overview}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \vspace{-20pt}
    \caption{
      \textbf{\sys's speedup for \ttiny{width=}2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) \todo{Blocking Eager}, only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) \todo{No Eager}: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
  % \kk{FUTURE: Run and show all plots (with and without split for all experiments.)}
}
    \vspace{-14pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

\heading{Results}
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for 31 pipelines, with \ttt{width=}16 and 10GB inputs.
It does not include 3 pipelines that use \ttt{head} fairly early thereby finishing execution in under $0.1$ seconds.
We refer to each pipeline using its x-axis index in Fig.~\ref{fig:unix50-individual}.
% The script index refers to the challenge level, in both the plots and the discussion.
% \kk{The above is not exactly true since we sorted them. If someone goes to take a look at the solution source they will be confused.}
Average speedup is \todo{$6.02\times$}, % median is $6.48\times$, 
  and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},

@@

\heading{Take-aways}
\sys can be applied to programs of notable size \todo{and complexity} to offer significant acceleration.
A broader take-away is that \sys is also able to extract parallelism from fragments that are not purely compute-intensive, \ie the usual focus of conventional parallelization systems.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/pash_overview.pdf}}
\caption{
  \textbf{\sys overview.}
  \sys identifies dataflow regions~\sx{dataflow-regions}, 
  converts them to dataflow graphs~\sx{graph-components},
  applies transformations~\sx{ir:transformations} based on the parallelizability properties  of the commands in these regions(\S\ref{cmd}, \S\ref{ext}),
  and emits a parallel script that uses custom primitives~\sx{optimizer}.
}
\vspace{-18pt}
\label{fig:overview}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \vspace{-20pt}
    \caption{
      \textbf{\sys's speedup for \ttiny{width=}2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) Blocking Eager: only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) No Eager: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
  % \kk{FUTURE: Run and show all plots (with and without split for all experiments.)}
}
    \vspace{-14pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

\heading{Results}
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for 31 pipelines, with \ttt{width=}16 and 10GB inputs.
It does not include 3 pipelines that use \ttt{head} fairly early thereby finishing execution in under $0.1$ seconds.
We refer to each pipeline using its x-axis index in Fig.~\ref{fig:unix50-individual}.
% The script index refers to the challenge level, in both the plots and the discussion.
% \kk{The above is not exactly true since we sorted them. If someone goes to take a look at the solution source they will be confused.}
Average speedup is $6.02\times$, % median is $6.48\times$, 
  and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},

@@

\heading{Take-aways}
\sys can be applied to programs of notable size and complexity to offer significant acceleration.
A broader take-away is that \sys is also able to extract parallelism from fragments that are not purely compute-intensive, \ie the usual focus of conventional parallelization systems.
